Motion planning for assessing accessibility of protein tunnels

### 2017-09-05 paper.tex
sota

RRT-based planners cannot cope with the narrow passage problem simply by increasing the probability of sampling in them, as the
growth of the configuration tree may be toward the random samples may be blocked by obstacles~\cite{vonasekphd}.
Instead, the random samples has to be generated in the difficult regions only if the tree can approach them.
This is the main idea of the guided sampling~\cite{vonasek2009rrt,denny2014marrt,denny2016dynamic}, where a the configurations
space is sampled with higher probability around a given list of configurations.
These guiding configurations can be computed e.g. as a path in the workspace.
Authors of~\cite{kardossRRTKK} proposed to place the guiding configurations between difficult and easy regions of the configuration space, but
they did not proposed any strategy to find the waypoints.

@@

%Both tested ligands have more than 10 atoms and therefore they cannot fit into the tunnel of with 0.9~\AA, so
%the radii of ligands were scaled down. 
Four different scaling-down factors were used: $\smin=\{0.4,0.5,0.6,0.7\}$.
For each scale, 20 collision-free initial configurations were found in the $\RI=2$\AA\ radius around the first sphere of the tunnel (outside the protein).
For each ligand, each minimal scale $\smin$ and each initial configuration, 10 trajectories were computed using the proposed planner.
The parameters of the planner were: $\Imax=10,000$, $m=50$, $\gb=0.9$, $\dt=1.5$\AA, $\rv=2$~\AA.
For each initial configuration, the success rate is computed as the ratio of trajectories that reached the end of the tunnel (to the distance 
 $\rv=2$~\AA or less) over 100 trials.

@@

>>>>

RRT-based planners cannot cope with the narrow passage problem simply by increasing the probability of sampling in them, as the
growth of the configuration tree may be toward the random samples may be blocked by obstacles~\cite{vonasekphd}.
DD-RRT~\cite{yershovaDDRRT} limits the selection of nodes for expansion to a small ball. 
The radius of a ball is defaulty infinity, but if the node cannot be expanded, it is set to a predefied (small) value.
This small radius can be adapted according to the success rate of the expansion in ADD-RRT~\cite{jailletADRRT}.
To attract the tree towards a region, the random samples have to be generate there only if the tree can expand to the region.
This is the main idea of the guided sampling~\cite{vonasek2009rrt,denny2014marrt,denny2016dynamic}, where a the configurations
space is sampled with higher probability around a given list of configurations.
These guiding configurations can be computed e.g. as a path in the workspace.
Authors of~\cite{kardossRRTKK} proposed to place the guiding configurations between difficult and easy regions of the configuration space, but
they did not proposed any strategy to find the waypoints.

@@

%Both tested ligands have more than 10 atoms and therefore they cannot fit into the tunnel of with 0.9~\AA, so
%the radii of ligands were scaled down. 
Four different scaling-down factors were used: $\smin=\{0.5,0.6,0.7,0.8\}$.
For each scale, 20 collision-free initial configurations were found in the $\RI=2$\AA\ radius around the first sphere of the tunnel (outside the protein).
For each ligand, each minimal scale $\smin$ and each initial configuration, 10 trajectories were computed using the proposed planner.
The parameters of the planner were: $\Imax=10,000$, $m=50$, $\gb=0.9$, $\dt=1.5$\AA, $\rv=2$~\AA.

For each initial configuration, the success rate is computed as the ratio of trajectories that reached the end of the tunnel (to the distance 
 $\rv=2$~\AA or less) over 100 trials.

@@

The results are shown in Tab.~\ref{tab::main}.

\begin{table}
\centering
\caption{\label{tab::main}Traversability of the tunnels}
\small
\renewcommand{\tabcolsep}{1pt}
{\small
\input graph.tex
}
\end{table}
